\chapter*{Acknowledgements}

The history of scientific and technological progress is full of examples of visionaries whose contributions were rejected by the scholar community or mocked by the press of the time for being too fanciful or belonging to the realm of fantasy and deemed impossible. While this fact might come as non surprising for many, in writing this thesis I have found particular examples of astonishing significance which have made me feel both an enormous embarrassment and an incommensurable admiration, being the 1920 editorial of The New York Times dismissing Robert H. Goddard ideas for space propulsion (and its correction one day after the Eagle successfully landed on the moon, 49 years later) a somewhat recent, paradigmatic example. I would like to express my gratitude to all those determined, brilliant individuals for being a source of inspiration for the generations that followed them.

Open source software is no exception to this rule, with the additional handicap that most software that we take for granted today has been (or continues to be) developed by volunteers against all odds and without specific funding in their free time, when their children are sleeping or as pure procrastination during their full time jobs. This Master thesis would not be possible without the tremendous, often unpaid and unrecognized effort of all those volunteers, to whom I also express my greatest thankfulness.

In writing this thesis I have lost countless hours looking for old but valuable scientific papers and books that were impossible to find (not even available for purchase) despite all my best efforts, which, to all effects and in my humble opinion, can be considered as disastrous as the destruction of the Library of Alexandria. The academic publishing industry naturally holds accountable for this regretful loss of human knowledge. I would like to thank from the bottom of my heart all the people that have left behind this fallacious system that hinders human progress and that have openly shared all their knowledge, for free. In return of all that wisdom and as my very modest contribution, this Master thesis has been written in English to serve a bigger audience and published in the open.

Moving now to more personal acknowledgements, I would like to thank my advisor, professor Manuel Sanjurjo, for all the tremendous patience and support he has shown since this thesis started. I am sure mentoring a student that occasionally finds some time on weekends to do real work is not an easy task. Many thanks to David Morante as well, and also to my \textit{de iure} supervisor, professor Jesús Peláez, for clearing all the administrative obstacles. I would like to mention Helge Eichhorn and Frazer McLean as well, who helped me shape the original \verb|poliastro| paper.

Going back in time a little bit more, I cannot omit Mario Merino from this list. During my freshman year he showed true dedication for his students, helping those in need, encouraging collaboration among them and motivating us to go beyond what was expected for us. His vision for a better University has inspired me ever since, and his always kind advice was determinant for me to apply for an Erasmus scholarship, which still is the best decision I have ever made. It is possible to be a genius and still have time for the rest of us, and Mario taught us so. 

Internal motivation is a necessary condition for successfully accomplishing any task, but external motivation is, no doubt, an invaluable help. I would like to thank my friends and coworkers for encouraging me in the final stages of writing this thesis, especially Lourdes, who sparked the determination I still needed despite everything was in place, and my good friend Álex, for his always accurate insights and for making this Python journey a worthwhile, entertaining experience.

I cannot finish these acknowledgements without thanking my parents for making sure I could have all the opportunities I wanted. This is as sincerest as it can be, for I know there is no such thing as a "self-made person" and I have enjoyed privileges that others can only dream of, thanks to a great extent to my family. \textit{Papá, mamá, hermano, muchas gracias por todo}.

Lastly, I would also like to thank professor Michèle R. Lavagna in a very special way for giving me freedom to start this project four years ago in Milan, Italy, and for accepting my negative to take the final oral exam, effectively failing my favourite subject, ever. \textit{Grazie mille per tutto}.